Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-03 manuscripts/manuscript.tex
update tex

\begin{verbatim}
## module glm loaded
\end{verbatim}

\begin{verbatim}
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
\end{verbatim}

\begin{verbatim}
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
\end{verbatim}

@@

\begin{equation}
V_t(X_t) = \max_{h_t} \left{ R(h_t, X_t) + \delta \cdot \mathbf{\mathrm{E}}_{X_t+1} \left[ V_{t+1}( X_{t+1}) | X_t, h_t \right] \right}
\end{equation}

@@

\includegraphics{./manuscript_files/figure-latex/figure_1.pdf}

@@

\% latex table generated in R 3.1.0 by xtable 1.7-3 package \% Mon Jun 2
17:34:16 2014

@@

\includegraphics{./manuscript_files/figure-latex/figure_2.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_3.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_4.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_5.pdf}

@@

\begin{verbatim}
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
\end{verbatim}

\includegraphics{./manuscript_files/figure-latex/figure_6.pdf}

@@

\begin{verbatim}
## Loading required package: grid
\end{verbatim}

\includegraphics{./manuscript_files/figure-latex/figure_7.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S1.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S2.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S3.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S4.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S5.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S6.pdf}

@@

\includegraphics{./manuscript_files/figure-latex/figure_S7.pdf}

\includegraphics{./manuscript_files/figure-latex/figure_S8.pdf}

@@

\begin{verbatim}
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
## Using V1 as value column: use value.var to override.
## No id variables; using all as measure variables
\end{verbatim}

\begin{verbatim}
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
## stat_bin: binwidth defaulted to range/30. Use 'binwidth = x' to adjust this.
\end{verbatim}

\includegraphics{./manuscript_files/figure-latex/figure_S9.pdf}

>>>>

@@

\begin{equation}
V_t(X_t) = \max_{h_t} \lbrace R(h_t, X_t) + \delta \cdot \mathbf{\mathrm{E}}_{X_t+1} \left[ V_{t+1}( X_{t+1}) | X_t, h_t \right] \rbrace
\end{equation}

@@

\includegraphics{components/figure/manuscript-figure_1.pdf}

@@

\% latex table generated in R 3.1.0 by xtable 1.7-3 package \% Tue Jun 3
13:34:19 2014

@@

\includegraphics{components/figure/manuscript-figure_2.pdf}

@@

\includegraphics{components/figure/manuscript-figure_3.pdf}

\includegraphics{components/figure/manuscript-figure_4.pdf}

@@

\includegraphics{components/figure/manuscript-figure_5.pdf}

@@

\includegraphics{components/figure/manuscript-figure_6.pdf}

@@

\includegraphics{components/figure/manuscript-figure_7.pdf}

@@

\includegraphics{components/figure/manuscript-figure_S1.pdf}

\includegraphics{components/figure/manuscript-figure_S2.pdf}

@@

\includegraphics{components/figure/manuscript-figure_S3.pdf}

\includegraphics{components/figure/manuscript-figure_S4.pdf}

@@

\includegraphics{components/figure/manuscript-figure_S5.pdf}

\includegraphics{components/figure/manuscript-figure_S6.pdf}

@@

\includegraphics{components/figure/manuscript-figure_S7.pdf}

\includegraphics{components/figure/manuscript-figure_S8.pdf}

@@

\includegraphics{components/figure/manuscript-figure_S9.pdf}
